Object Search with a Mobile Device for the Visually Impaired\\Using an Active Guidance System

### 2018-11-21 paper.tex
new title/abstract and some fixes

\title{Designing an Agent for an Active Guidance System for Object Search}

@@

\keywords{Active vision, object search, vision impaired, Markov decision process}

\abstract{In this work, we propose a Markov Decision Process-based system that generates guidance instructions for a user to find a target object in an unknown environment and forms part of an active vision indoor guidance system for the visually impaired. An initial implementation of this system was implemented in an Android app and a set of experiments were carried out with sighted participants to determine its effectiveness. We found that the system works reasonably well and compares well to similar systems. }

@@

\section{\uppercase{Future Work and Conclusion}}\label{sec:conclusion}

@@

\clearpage
\bibliographystyle{apalike}
\bibliography{bib}

>>>>

\title{Object Search with a Mobile Device for the Visually Impaired\\Using an Active Guidance System}

@@

\keywords{Active vision, object search, vision impairment, Markov Decision Process}

\abstract{Nowadays, smartphones can be used to provide a multitude of services to assist people with visual impairments. The cameras embedded in these mobile devices, in particular, can be used for many useful tasks, including searching particular objects in unknown environments. Although previous research in computer vision has looked at ways to solve these tasks by processing the video frames of the mobile camera, very little work has been done in {\em actively} guiding the user towards specific point of interest that maximise the effectiveness of the underlying visual algorithms.
In this paper, we propose a control algorithm based on a Markov Decision Process (MDP) that generates instructions, in real-time, to guide a user searching for a target object with a smartphone's camera. The solution is part of a more general active vision application for the visually impaired. An initial implementation of the system on an Android smartphone was experimentally evaluated with sighted participants to determine the performance of the control algorithm. The results show the effectiveness of our solution and its potential application to help the visually impaired find objects in unknown environments.}

@@

\section{\uppercase{Conclusions}}\label{sec:conclusion}

@@

% \clearpage
\bibliographystyle{apalike}
\bibliography{bib}
